\SW: II. Did we beat the lens finding robots in CFHTLS?

### 2014-11-04 doc/sw-cfhtls.tex
rearranged and added many sections and figures but are not yet final

The CFHT Legacy Survey has been searched for strong lenses with
semi-automated algorithms both at galaxy and groups scales. With the aim
of improving these lens finding robots, we carry out a blind lens search
in the complete \cfhtls WIDE survey with \sw. We describe the training
sample used for both training the citizen scientists that participated
in \sw and calibrating their performance. We generate realistic looking
simulated samples of lenses both at galaxy and group-scales as part of
this training sample. We present 80 new strong gravitational lens
candidates discovered from the \sw-\cfhtls search out of which 40
candidates are promising. Furthermore, we compile a sample of false
positives which can be used for robot testing, first of its kind for the
lensing community. The simulated sample is also used to make a
comparison between human performance against the robots. We find that
the XX per cent of the known lens sample is recovered and the new lens
sample has XX completeness with respect to the simulated sample. We make
available the following data products: simulated sample, simulation code
and the false positives sample at XXX.

@@

The Canada-France-Hawaii Telescope Legacy Survey (CFHTLS) is a
photometric survey in five optical bands ($u^*g'r'i'z'$) carried out
with the wide-field imager MegaPrime which has a 1~deg$^2$ field-of-view
and a pixel size of 0.186\arcsec. The \cfhtls WIDE covers a total area
of 171~deg$^2$ on the sky and it consists of four fields W1, W2, W3 and
W4. The field W1 has the largest sky coverage of 63.65~deg$^2$. The
fields W2 and W4 have similar sky coverages of 20.32~deg$^2$ and
20.02~deg$^2$, respectively\footnote{These numbers are estimated from http://terapix.iap.fr/cplt/table\_syn\_T0006.html}.
The field W3 has a sky coverage of 42.87~deg$^2$ and is more than twice
as large as W2 and W4.

@@

@@

%magdiff=5*0.1;
%zdiffq=0.1;
\begin{figure*}
\begin{center}
\includegraphics[scale=0.85]{sw-cfhtls-figs/distrib_remu.pdf}
\caption{ \label{fig:remudist}
Einstein radius distribution for all types of lenses. The dashed-dotted (blue)
curves show the theoretical prediction assuming an SIS model at galaxy-scales
and a total (NFW+Hernquist) model at groups-scales taken from \citep{More2012}.
}
\end{center}
\end{figure*}

@@

%\begin{figure*}
%\begin{center}
%\includegraphics[scale=0.95]{sw-cfhtls-figs/distrib_srczmag.eps}
%\caption{ \label{fig:szmdist}
%Redshift distribution on the left and magnitude distribution on the right of the
%simulated sample for the background sources. The different types of lines show the
%distribution correspond to the three types of simulated lenses galaxy-quasar,
%galaxy-galaxy and group-galaxy. 
%}
%\end{center}
%\end{figure*}
%
%
%\begin{figure}
%\begin{center}
%\includegraphics[scale=0.95]{sw-cfhtls-figs/distrib_reff.eps}
%\caption{ \label{fig:reffdist}
%Distributions of magnification (left) and source effective radius in units of
%pixel (right).
%}
%\end{center}
%\end{figure}

@@

@@

\subsection{Discovery of new lenses from \sw}
\label{sec:results:disc}

\begin{figure*}
\begin{center}
\includegraphics[scale=1.5]{sw-cfhtls-figs/lenscand_2p0_3p0.pdf}
\caption{ \label{fig:lch1}
Sample of high probability lens candidates ($R_{avg}>=2.0$).
}
\end{center}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[scale=1.5]{sw-cfhtls-figs/lenscand_1p3_1p7.pdf}
\caption{ \label{fig:lcl}
Sample of medium probability lens candidates ($1.0<R_{avg}<2.0$).
}
\end{center}
\end{figure*}

@@

\subsection{Recovery of known \cfhtls lenses from \sw}
\label{sec:results:reco}

@@

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % 
\subsection{\cfhtls completeness and purity}
\label{sec:results:sample}

@@

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % 
\subsection{Stage 1 Classification}
\label{sec:results:stage1}

\subsection{Stage 2 Classification}
\label{sec:results:stage2}

\subsection{Comparison with ``Expert'' Classification}
\label{sec:results:experts}

@@

@@

}

We looked at the locations of simulated and real lenses from our data
those were missed by \sw compared to the locations of the lenses that
got detected. The real lens sample consists of a total of 383 candidates
which have $P_l>2.e-5$ and received a rank of $R_{avg}>0$ from the
expert. We do not find any obvious dependency in the rate of detections
as a function of the position of a given lens for both simulated and
real lens sample. Thus, the completeness of the lens sample is not
affected by whether a lens is located close to the border or well within
the center (see  Figure~\ref{fig:comppos}).

@@

\input{acknowledgments.tex}
This work is based on observations obtained with MegaPrime/MegaCam, a joint
project of CFHT and CEA/IRFU, at the Canada-France-Hawaii Telescope (CFHT) which
is operated by the National Research Council (NRC) of Canada, the Institut
National des Sciences de l'Univers of the Centre National de la Recherche
Scientifique (CNRS) of France, and the University of Hawaii. This research used
the facilities of the Canadian Astronomy Data Centre operated by the National
Research Council of Canada with the support of the Canadian Space Agency.
CFHTLenS data processing was made possible thanks to significant computing
support from the NSERC Research Tools and Instruments grant program.
This work was supported by World Premier International Research Center
Initiative (WPI Initiative), MEXT, Japan.

>>>>

The CFHT Legacy Survey has been searched for strong lenses with
semi-automated algorithms both at galaxy and groups scales. With the aim
of improving these lens finding robots, we carry out a blind lens search
in the complete \cfhtls \textsc{wide} survey with \sw. We describe the training
sample used for both training the citizen scientists that participated
in \sw and calibrating their performance. We generate realistic looking
simulated samples of lenses both at galaxy and group-scales as part of
this training sample. We present 80 new strong gravitational lens
candidates discovered from the \sw-\cfhtls search out of which 40
candidates are promising. Furthermore, we compile a sample of false
positives which can be used for robot testing, first of its kind for the
lensing community. The simulated sample is also used to make a
comparison between human performance against the robots. We find that
the XX per cent of the known lens sample is recovered and the new lens
sample has XX completeness with respect to the simulated sample. We make
available the following data products: simulated sample, simulation code
and the false positives sample at XXX.

@@

The Canada-France-Hawaii Telescope Legacy Survey (CFHTLS) is a
photometric survey in five optical bands ($u^*g'r'i'z'$) carried out
with the wide-field imager MegaPrime which has a 1~deg$^2$ field-of-view
and a pixel size of 0.186\arcsec. The \cfhtls \textsc{WIDE} covers a total area
of 171~deg$^2$ on the sky and it consists of four fields W1, W2, W3 and
W4. The field W1 has the largest sky coverage of 63.65~deg$^2$. The
fields W2 and W4 have similar sky coverages of 20.32~deg$^2$ and
20.02~deg$^2$, respectively\footnote{These numbers are estimated from http://terapix.iap.fr/cplt/table\_syn\_T0006.html}.
The field W3 has a sky coverage of 42.87~deg$^2$ and is more than twice
as large as W2 and W4.

@@

\begin{figure}
\begin{center}
\includegraphics[scale=1.0]{sw-cfhtls-figs/distrib_remu.pdf}
\caption{ \label{fig:remudist}
Einstein radius distribution for all types of lenses. The dashed-dotted (blue)
curves show the theoretical prediction assuming an SIS model at galaxy-scales
and a total (NFW+Hernquist) model at groups-scales taken from \citep{More2012}.
}
\end{center}
\end{figure}

@@

%magdiff=5*0.1;
%zdiffq=0.1;

@@

%
%\begin{figure}
%\begin{center}
%\includegraphics[scale=0.95]{sw-cfhtls-figs/distrib_reff.eps}
%\caption{ \label{fig:reffdist}
%Distributions of magnification (left) and source effective radius in units of
%pixel (right).
%}
%\end{center}
%\end{figure}

@@

\subsection{\sw Lens Sample}

\subsubsection{Selection of \sw lens candidates}
\label{sec:results:stage1}

\begin{figure}
\begin{center}
\includegraphics[scale=1.0]{sw-cfhtls-figs/poffl_expr_ncl.pdf}
\caption{ \label{fig:comp_exp} Comparison of the P(lens) with the expert
grades and number of classification for each subject.  }
\end{center}
\end{figure}

\subsection{New lens candidates from \sw}
\label{sec:results:disc}

{\bf \textcolor{red} {CHANGE THE TABLE, CHECK IF ALL FIGS ARE UPDATED,
ADD ISD PLOT, CHECK FOR STAGE 1 -- COMPLETENESS OF SIMS AND KNOWN LENSES
and P value comparison, what about the duplicate lenses near the borders
- stats on those?, MAKE A STATS TABLE that gives various numbers and
fractions of (new and known) lens candidates detected at stages 1 and 2.}}

\begin{table}
\begin{center}
\caption{ \label{tab:stats} 
Statistics of detections in \sw }
\begin{tabular}{l l l l l l}
\hline
   &  \multicolumn{2}{c} {Stage I}  & \multicolumn{3}{c}{Stage II} \\ 
      & KnCa  &  KnCo  & KnCa & KnCo & NeCa \\
\hline
\hline
Number  & 1.0 & 1.0 & 1.0  & 1.0  & 1.0 \\
Fraction  & 1.0 & 1.0 & 1.0 & 1.0 & 1.0 \\
P(lens) & 0.95 & 0.95 & 0.3 & 0.3 & 0.3 \\

\hline
\end{tabular}
\end{center}
{KnCa}-- Known lens candidates \\
{KnCo}-- Known confirmed lenses \\
{NeCa}-- New lens candidates  \\
\end{table}

@@

\begin{figure*}
\begin{center}
\includegraphics[scale=1.5]{sw-cfhtls-figs/lenscandfin.pdf}
\caption{ \label{fig:lch1}
Sample of lens candidates with $R_{avg}>=1.3$.
}
\end{center}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[scale=1.5]{sw-cfhtls-figs/lenscandfin_1.pdf}
\caption{ \label{fig:lcl}
Sample of lens candidates $R_{avg}>=1.3$.
}
\end{center}
\end{figure*}

@@

\subsection{Recovery of known \cfhtls lenses with \sw}
\label{sec:results:known}

@@

\begin{figure}
\begin{center}
\includegraphics[scale=1.0]{sw-cfhtls-figs/comp_reinst.pdf}
\caption{ \label{fig:compre} Completeness of simulated and known lens
samples based on the final \sw sample. }
\end{center}
\end{figure}

@@

\subsection{Image separation distribution}
\label{sec:results:isd}

\begin{figure}
\begin{center}
\includegraphics[scale=1.0]{sw-cfhtls-figs/isd_cfhtls_sw.pdf}
\caption{ \label{fig:isd} Image separation distribution. Comparing
theoretical predictions with the \cfhtls known lens samples (REF) and
the same \cfhtls sample after combining with the incremental lens sample
from \sw }
\end{center}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[scale=1.0]{sw-cfhtls-figs/zlens_reinst.pdf}
\caption{ \label{fig:zlre}
Comparison of Lens redshift and Arc radius for all three lens samples,
namely, from \sw, SARCS and those from the RingFinder.}
\end{center}
\end{figure}

@@

}
\subsection{Blind Lens Search}
We looked at the locations of simulated and real lenses from our data
those were missed by \sw compared to the locations of the lenses that
got detected. The real lens sample consists of a total of 383 candidates
which have $P_l>2.e-5$ and received a rank of $R_{avg}>0$ from the
expert. We do not find any obvious dependency in the rate of detections
as a function of the position of a given lens for both simulated and
real lens sample. Thus, the completeness of the lens sample is not
affected by whether a lens is located close to the border or well within
the center (see  Figure~\ref{fig:comppos}).

@@

\input{acknowledgments.tex}
This work is based on observations obtained with MegaPrime/MegaCam, a joint
project of CFHT and CEA/IRFU, at the Canada-France-Hawaii Telescope (CFHT) which
is operated by the National Research Council (NRC) of Canada, the Institut
National des Sciences de l'Univers of the Centre National de la Recherche
Scientifique (CNRS) of France, and the University of Hawaii. This research used
the facilities of the Canadian Astronomy Data Centre operated by the National
Research Council of Canada with the support of the Canadian Space Agency.
CFHTLenS data processing was made possible thanks to significant computing
support from the NSERC Research Tools and Instruments grant program.
